\begin{acknowledgements}

There is a seemingly countless number of people I want to acknowledge who have supported me throughout my time in graduate school. 

\vspace{-\topsep}
\begin{itemize}
\setlength{\parskip}{0pt}
 \setlength{\itemsep}{0pt plus 1pt}
\item[--] Family: Thank you mummy and fasha for giving birth to me. You did a great job.
\item[--] PhD Committee: Thank you for all of your time, advice, and for putting up with all of my questions--both the smart and the dumb ones.
\item[--] Steve Gaines: You were my Thanksgiving toast. I'm so thankful for you.
\item[--] Hunter Lenihan: Even though our paths diverged, thank you for all of the lessons you taught me.
\item[--] My roommates: My roommates, my psuedo family, and my ``German friends". I love and thank you so much for everything you've done for me. House Dad (Spencer), House Child (Katrina), and House Goldfish (Mark), don't die without your House Mom. She's really going to miss you.
\item[--] Cubicle mate: Thank you Brian for all of the puns, for being an awesome study buddy through all of the PSTAT classes we took together, for being a patient sounding board to run ideas by, and for listening to me vent all my frustrations. Someday we'll win the lottery.
\item[--] Past and current lab mates: Thank you for all of your support the hugs and the listening. I'll always have chocolate for you.
\item[--] Bren buddies: Special shout out to Ian and Timbo. Thanks guys!
\item[--] Bren staff: Thank you Sage for all of your help my first year. Thank you Corlei, I know you no longer are at Bren, but you helped me so much when you were at Bren. You were the ultimate Bren Mom. Thank you Dee for being so helpful and a sweetheart. Thank you Kim for being the wonderful, unique you. Never change. Thank you Casey for being a friend in need. Thank you Kristine for being so supportive. Thank you Satie for guiding me along the way. Thank you Onella and Yoda. I loved getting to know you both. Thank you Doris for answering all of my emails. Sorry to bombard you all the time. Thank you Dave for all of your career advice. Thank you Geoff, Brad, and Steve for all of your computer help. Thank you Beth for joining me at all of our pro fem events. Fun times. Thank you Lisa for always taking the time to help me, no matter how busy you were. I really appreciate everything you've done for me.
\item[--] Bren faculty: Thank you Andrew Plantinga. I had a great experience working with you as a mentor on the MESM GP. Thank you Sarah Anderson for being super supportive. 
\item[--] PSTAT faculty: Thank you Prof. Jammalamadaka for being the professor of me dreams. I will always remember your catch phrase, ``Let's see what's cooking!" Thank you for Prof. Wang for being such a great teacher. I really enjoyed your lectures. Thank you Prof. Hsu. I still remember the time you thought I was doing my PhD in the PSTAT Department. I was so flattered. 
\item[--] PSTAT staff: Thank yooou Jamie. You're the best.
\item[--] NOAA/IATTC staff: Thank you Hoo Hoo and Carolina for always taking the time to help me.
\item[--]ERI staff: Thank you Erik Fields, St\'ephane Maritorena, and Dave Siegel for all of your help with SeaWiFS. 
\item[--] Ladies crew: Ladies, I love and appreciate you so much. I can't even put in words how much you mean to me. Timnit, Jessica, Phoebe, Julia, Lewam, and Alice. So much love going your way.
\item[--] Potluck and karaoke buddies: Mengya, Yuwei, Rungsheng, Ying, Yang, Jiajia, Zhitong, and Yuxiong--I've had such a great time hanging out with all of you. I've enjoyed all of our time together as friends. 
\item[--] Non-Bren grad school friends: Tara/Yuanbo, Zach, Ya, Anna, Sergio, and Ben--thank you for being such great friends and for all of the laughs.  Cool, cool.
\item[--] My mentors: Matt Burgess and Cody Szuwalski--I'm wishing the best for you in all of your endeavors.
\item[--] The Chalet Crew: Jen, Carl, Myley, Matt, Molly, Jacquie, Joe, and Mike--I've never been a group person, but you changed my mind
\item[--] Graduate Scholars family: my lovely mentoring family: Timnit, Terence, Natasha, and Xochitl and the GSP faculty and staff: Carlos, Michele, and Miros. I'm always here for you even if we are far apart.
\item[--] Other UCSB folks: Lana Hale-Smith and Megan Unden - I love you ladies. Thank you for being so helpful and validating.
\item[--] Thank you Deborah and Hap for being amazing role models and mentors.
\item[--] Funding sources: Dr. Daniel Vapnek Fellowship and Award, NMFS-Sea Grant Fellowship in Population and Ecosystem Dynamics (NOAA Grant $\#NA14OAR4170211$, California Sea Grant College Program Project $\#E/PD-13$), the Bren School, and the PSTAT Department.
\item[--] To all the dogs I ever dog sat--never forget me. And the owners too. Thanks for letting me get my doggo snuggles.
\end{itemize}
\vspace{-\topsep}

\end{acknowledgements} 